Working memory performance in adverse environments: Enhanced, impaired, or intact?

### 2024-06-25 README.Rmd
new top-level README file

Below is an overview of all the project milestones, such as first-time data access, submissions, and revisions.
Data access events were automatically captured using custom code, which over the course of this project was collected in the R package `projectlog` [https://stefanvermeent.github.io/projectlog/](https://stefanvermeent.github.io/projectlog/).
For more information about how tracking worked, Go to the [Open science workflow tab](https://stefanvermeent.github.io/abcd_ddm/opensci_workflow/README.html).

```{r results ='asis', echo = FALSE}
milestones <- gert::git_tag_list() |> 
  mutate(
    tags = pmap(list(name = name, ref = ref, commit = commit), function(name, ref, commit) {
      gert::git_commit_info(commit) |> 
        as_tibble() |> 
        select(commit = id, author, time, message) 
    })
  ) |> 
  select(-commit, -ref) |> 
  unnest(tags) |> 
  separate(message, into = c("description", "hash", "code"), sep = "\\n") |> 
  mutate(
    name = map_chr(name, function(name) {
      name |> 
        str_remove("\\[\\[") |>
        str_remove("\\d*$") |> 
        str_replace("_", " ") |> 
        str_to_title()
    })
  ) |> 
  mutate(
    code = str_remove_all(code, "^code\\s") |> str_replace_all(string = _, "\\|\\>", "\\|\\>\\\n"),
    link_to_git = paste0(
       gert::git_remote_list()$url |> str_remove(string = _, pattern = "\\.git$"), "/tree/", commit)
    ) |>
  arrange(desc(time))

# Write scripts including code to .projectlog folder
milestones |> 
  pwalk(function(name,commit,author,time,description,hash,code,link_to_git){

@@

      url <- gert::git_remote_list()$url |> 
        str_remove(string = _, "\\.git$") |> 
        paste0(paste0("/commit/", commit))

      #  url <- "<anonymized repository>"

@@

branch <- gert::git_branch_list() |> filter(local == TRUE) |> pull(name)

>>>>

Below is an overview of all the project milestones, such as first-time data access, submissions, and revisions.
Data access events were automatically captured using custom code, which over the course of this project was collected in the R package `projectlog` [https://stefanvermeent.github.io/projectlog/](https://stefanvermeent.github.io/projectlog/).

```{r results ='asis', echo = FALSE}
milestones <- gert::git_tag_list() |> 
  mutate(
    tags = pmap(list(name = name, ref = ref, commit = commit), function(name, ref, commit) {
      gert::git_commit_info(commit) |> 
        as_tibble() |> 
        select(commit = id, author, time, message) 
    })
  ) |> 
  select(-commit, -ref) |> 
  unnest(tags) |> 
  separate(message, into = c("description", "hash", "code"), sep = "\\n") |> 
  mutate(
    branch = gert::git_branch_list() |> filter(local == TRUE) |> pull(name),
    name = map_chr(name, function(name) {
      name |> 
        str_remove("\\d*$") |> 
        str_replace("_", " ") |> 
        str_to_title()
    }),
    code = ifelse(name == "Data Access", str_remove_all(code, "^code\\s") |> str_replace_all(string = _, "\\|\\>", "\\|\\>\\\n"), "Not applicable"),
    link_to_git = ifelse(name == 'Data Access', 
                         paste0(get_git_url(), "/blob/", branch, "/", commit, ".R"),
                         paste0(get_git_url(), "/tree/", commit)
    ),
    hash = ifelse(name != "Data Access", "Not applicable", hash),

    ) |>
  arrange(desc(time))

# Write scripts including code to .projectlog folder
milestones |> 
  pwalk(function(name,commit,author,time,description,hash,code,branch,link_to_git){

@@

      url <- get_git_url() |> 
        paste0("/commit/", commit)

@@
